TRITON: Globally Consistent Sim-to-Real Transfer

### 2022-06-02 paper.tex
Moved things

\title{TRITON: Torwards Globally Consistent Sim-to-Real Transfer}

@@

Please read the instructions below carefully and follow them faithfully.

@@

Papers to be submitted to NeurIPS 2022 must be prepared according to the
instructions presented here. Papers may only be up to {\bf nine} pages long,
including figures. Additional pages \emph{containing only acknowledgments and
	references} are allowed. Papers that exceed the page limit will not be
reviewed, or in any other way considered for presentation at the conference.

The margins in 2022 are the same as those in 2007, which allow for $\sim$$15\%$
more words in the paper compared to earlier years.

Authors are required to use the NeurIPS \LaTeX{} style files obtainable at the
NeurIPS website as indicated below. Please make sure you use the current files
and not previous versions. Tweaking the style files may be grounds for
rejection.

>>>>

\title{TRITON: Globally Consistent Sim-to-Real Transfer}

@@

Text

@@

Text
